---
title: "week9LiveCode"
author: "Nalina"
date: "3/5/2019"
output: html_document
editor_options: 
  chunk_output_type: inline
---
# delete all that

This is an Rmarkdown document. I can type whatever I want.

**this is bold**
*this is italic*

###This will make the font bigger

##This will make the font smaller 

Use setting button next to the Knit to set preview

Command opt i -> short cut for code 

```{r,warning=FALSE,message=FALSE,echo=TRUE}
library(viridis)
suppressPackageStartupMessages(library(tidyverse))
library(ggplot2)
glimpse(storms)
ggplot(data=storms)+
  geom_jitter(aes(x=as.factor(month),y=pressure, fill = wind), pch=21, alpha=.05)+
  scale_fill_viridis_c()+
  theme_bw()+
  labs(title= "Hurricane", subtitle= "with Max Wind", x="month")
  
```
Fill the point depending on wind speed

Echo = False  not show the code
CANT download package in Rmarkdown


Writing out equations in Rmarkdown:

If you want to write an equation, you put $ on either side of it.

$\sum_{i=y}^n x_i$

```{r}
library(knitr)

kable(head(storms), caption = "Table using kable")
htmlTable::htmlTable(head(storms))

library(DT)
#make an interactive table
DT::datatable(storms)
```

```{r}
library(plotly)
ggplotly(
ggplot(data=storms)+
  geom_jitter(aes(x=as.factor(month),y=pressure, fill = wind), pch=21, alpha=.05)+
  scale_fill_viridis_c()+
  theme_bw()+
  labs(title= "Hurricane", subtitle= "with Max Wind", x="month")
)
```

