---
title: "week9_assignment_NalinaAiem.Rmd"
author: "Nalina"
date: "3/11/2019"
output: html_document
---

I am a first year Ph.D. student in Animal Behavior Graduate Group. My reseach questions will play around **how human activity affects social behavior in long-tailed macaques** (*Macaca fascicularis*).

I can't insert pics

Use the storms data (included in RStudio) to create a plotly graph of the relationship between wind and pressure, where the status of the storm is indicated by a color.

```{r}
library(dplyr)
library(tidyverse)
library(plotly)
ggplotly(
ggplot(data=storms)+
  geom_jitter(aes(x=wind,y=pressure, col = as.character(status)), pch=21, alpha=.05)+
  scale_fill_viridis_c()+
  theme_bw()
)
```

Create a table that identifies the mean wind, pressure, ts_diameter, hu_diameter of each status of storm (remember to remove NAs!). Use the package htmlTable. Round each mean to only two decimal places (Hint
look up the function round)

```{r}
library(knitr)
storm1<-storms %>% 
  drop_na() %>% 
  group_by(status) %>% 
  summarise(mwind=round(mean(wind),2), mpressure=round(mean(pressure),2), mts_diameter=round(mean(ts_diameter),2), mhu_diameter=round(mean(hu_diameter),2))

  htmlTable::htmlTable(storm1)
```

CHALLENGE Find the duration, in number of days, of every hurricane from 2010 and later, and then use one of the map functions from purrr to write a sentence saying “Hurricane X lasted Y days” for each of these storms. You can look for some help with these functions here and here.

I can't figure out by myself... have to look for the answer
```{r}
hurr_len <- storms %>% 
  filter(status == "hurricane", year >= 2010) %>% 
  group_by(name, year) %>% 
  summarise(num_days = diff(range(day)))

map2_chr(hurr_len$name,hurr_len$num_days, function (x,y) paste("Herricane" ,x,"lasts",y,"days"))
```

